What paradigms can webcam eye-tracking be used for? Attempted replications of five ``classic'' cognitive science experiments

### 2024-11-03 manuscript.Rmd
Merged author affiliation changes

affiliation:
  - id: '1'
    institution: Cognitive Science Department, Vassar College
  - id: '2'
    institution: Department of Cognitive & Information Science, University of California,
      Merced
  - id: '3'
    institution: Psychology Department, Macalester College
  - id: '4'
    institution: Department of Communication Sciences and Disorders, MGH Institute of Health Professions

@@

```{=tex}
\endgroup
```

>>>>

  affiliation:
  - id: '4'
    institution: Cognitive Science Department, Vassar College
  - id: '2'
    institution: Department of Cognitive & Information Science, University of California,
      Merced
  - id: '1'
    institution: Psychology Department, Macalester College
  - id: '3'
    institution: Department of Communication Sciences and Disorders, MGH Institute of Health Professions

@@

```{=tex}
\endgroup
```
\newpage

#Contributions

\newpage

#Acknowledgements

\newpage

#Funding information
Funding for this project was provided by the Vassar College Department of Cognitive Science (JdL) and

\newpage

#Competing interests
The authors have no competing interests to declare.

\newpage

#Supplemental material

\newpage

#Data accessibility statement

\newpage

#Figure titles and legends
